\bf Designing Modular Software: A Case Study in Introductory Statistics

### 2016-12-09 jcgs-paper-2016/cover_letter.Rmd
Final submission

@@

Attached you will find the newest revision of our paper, written in response to the feedback we received from the reviewers, the associate editor, and yourself.

We have attempted to restructure the paper to focus on general techniques for designing a modular software system, using intRo itself as a case study. In particular, we have re-written the title, abstract, and a substantial portion of the background to highlight this new direction.

In addition to the refocusing, we have also extended our review of other software systems, and emphasized the need that intRo addresses. Table 1 provides a somewhat subjective but thorough comparison of many "competing" software systems in terms of a number of qualities, including whether or not they are web-based, the level of extensibility, and the amount of functionality. We have also done our best to address the other minor comments that were raised in the second round of reviews.

We hope that this latest revision addresses the majority of the issues with the previous, and we welcome any further critiques or comments.

>>>>

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

@@

Attached you will find the newest revision of our paper. Contained is:

- **paper.pdf**, the non-blinded version of our paper
- **paper_source.zip**, the source files for our paper, which include:
    - **paper.tex**, the tex source
    - **images**, a directory of figures
    - **refs.bib**, the references
    - **paper.pdf**, a copy of the non-blinded version of our paper

We also have included **forms.zip**, which has the two requested forms signed, as well as **response.pdf**, which has our final reviewer response.

Let us know if there are any further concerns or requests.
